### 2019-09-04 manuscript/manuscript.tex
ms updates

% TODO
% - generate figures and write about them
% - Figure 2 has some overplotting issues.

@@

We first analyzed \textcite{Barghi2019-qy}, an evolve-and-resequence study with
ten replicate populations exposed to a high temperature lab environment and
evolved for 60 generations, and sequenced every ten generations. Using the
seven timepoints and ten replicate populations, we estimated a bias-corrected
genome-wide $6 \times 6$ temporal covariance matrix (a timepoint is lost in
calculating all adjacent allele frequency changes). This temporal covariance
matrix contains

$60 \times 60$ temporal-replicate variance-covariance matrix (see XXX for
details).

Since each replicate population was sequenced every ten generations,
the timepoints $t_0 = 0$ generations, $t_1 = 10$ generations, $t_2 = 20$
generations, etc., lead to observed allele frequency changes across ten
generation blocks, $\Delta p_{t_0}, \Delta p_{t_1}, \ldots, \Delta p_{t_6}$.
Consequently, the ten temporal covariance matrices for each of the ten
replicate populations have off-diagonal elements of the form $\cov(\Delta
p_{t_0}, \Delta p_{t_1}) = \cov(p_{t_1} - p_{t_0}, p_{t_2} - p_{t_1}) =
\sum_{i=0}^{10} \sum_{j=10}^{20} \cov(\Delta p_i, \Delta p_j)$. Each diagonal
element has the form $\var(\Delta p_{t_0}) = \sum_{i=0}^{t_0} \var(\Delta
p_{i}) + \sum_{i \ne j}^{t_0} \cov(\Delta p_{i}, \Delta p_{j})$, and is thus a
combination of the effects of drift and selection, as both the variance in
allele frequency changes and cumulative temporal autocovariances terms increase
the variance in allele frequency. With sampling each generation, one could more
accurately partition the total variance in allele frequency change
\parencite{Buffalo2019-io}; while we cannot directly estimate the contribution
of linked selection to the variance in allele frequency change here, the
presence of a positive observed covariance between allele frequency change can
only be caused linked selection. Overall, we expect observed temporal
covariances between timepoints to be weak, some fraction of the additive
genetic variance and linkage disequilibrium that creates temporal
autocovariance decays in the ten generations between sequencing.

@@

Averaging across replicate populations, we find positive temporal covariances
across time that are statistically significant (p < XXX) consistent with linked
selection acting to affect allele frequency changes over very short time
periods. We visualize these covariances in Figure \label{figure-1} (A), which
depicts the temporal covariances through time, for each of the five rows
covariance matrix.  Each row represents the temporal covariance $\cov(\Delta
p_s, \Delta p_t)$, between some initial reference generation $s$ (the row of
the matrix), and some later timepoint $t$ (the column of the matrix). For each
row, the covariances at first are positive, and then decay towards zero as
expected when directional selection affects linked variants' frequency
trajectories until ultimately linkage disequilibrium and additive genetic
variance for decay \parencite{Buffalo2019-io}. Note that per replicate, the
signal is a bit noisier; see Supplementary Figures XXX.

While the presence of positive temporal covariances is consistent with linked
selection affecting allele frequencies over time, this measure not easily
interpretable. Additionally, we can quantify the impact of linked selection on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. Since the total
variation in allele frequency change can be decomposed into variance and
covariance components, $\var(p_t - p_0) = \sum_{i \ne j} \cov(\Delta p_i,
\Delta p_j) / \var(p_t - p_0)$, and the covariances are zero when drift acts
alone, this is a lower bound on how much of the variance in allele frequency
change is caused by linked selection \parencite{Buffalo2019-io}. We call this
measure $G(t)$, which is the total effect of linked selection between the
initial generation $0$ and some later generation $t$, which can be varied to
see how this quantity grows through time. As with the temporal covariances, the
study design of \textcite{Barghi2019} leads our measure $G(t)$ to be even more
conservative, since the temporal covariances with each ten-generation block
between sequenced timepoints are not directly observable, and are not included
in the numerator of $G(t)$. Still, we find a remarkably strong signal that
greater than $20\%$ of total variation in allele frequency change over 60
generations is directly the result of linked selection.

% NOTE in supp. material why the average replicate G(t) looks lower than
% replicates.

@@

\begin{align}
  \label{eq:conv-corr}
  \mathrm{cor}(\Delta p_s, \Delta p_t) = \frac{\E_{A\ne B} \left( \cov(\Delta p_{s,A}, \Delta p_{t,B}) \right)}{\E_{A\ne B} \left( \sqrt{\var(\Delta p_{s,A}) \var(\Delta p_{t,B})} \right)}
\end{align}
%
where $A$ and $B$ here are two replicate labels.

We've calculated the convergent correlation for all rows of the replicate
covariance matrices, which unlike temporal covariance matrices have diagonal
elements that are also covariances (e.g. $\cov(\Delta p_{t,A}, \Delta
p_{t,B})$). Like temporal covariances, we visualize these through time (Figure
\ref{fig:figure-2} A), with each line representing the convergent correlation
from a particular reference generation $s$ as it varies with $t$ (shown on the
x-axis). In other words, each of the colored lines corresponds to the like
colored row of the convergence correlation matrix (upper left in Figure
\ref{fig:figure-2} A). We find these decay very quickly, from an initial
convergence correlation coefficient of about 0.1 (block bootstrap confidence
intervals XXX; see the note in Supplementary Material XXX why these are so
narrow), to around 0.01 within 20 generations.

A benefit of between-replicate covariances is unlike temporal covariances,
these can be calculated with only two sequenced timepoints and a replicated
study design. This allowed allowed us to assess the impact of linked selection
in driving convergent patterns of allele frequency change across replicate
populations in two other studies. First, we reanalyzed the selection experiment
of \textcite{Kelly2019-dc}, which evolved three replicate populations of
\emph{Drosophila simulans} for 14 generations in a novel laboratory
environment. Since each replicate was exposed to the same selection pressure
and share linkage disequilibria common to the original natural founding
population, we expected each of the three replicate populations to have
positive between-replicate covariances. We find all three pairwise
between-replicate covariances are positive and statistical significant (p <
XXX, estimated via block bootstrap). We estimate the convergent correlation
coefficient across these replicates as 0.36 ($95\%$ block-bootstrap confidence
interval $[0.31, 0.40]$).

@@

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed \parencite{Barghi2019-qy}, some temporal covariances appeared to
become negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This could be caused by advantageous fitness backgrounds
later becoming disadvantageous, either due to frequency-dependent selection,
recombination breaking up coupled beneficial and deleterious alleles, or an
environmental change in the direction of selection. However, the signal of a
change in the direction of selection localized to a particular region of the
genome may be washed out when we calculate genome-wide temporal covariances.
Averaging over such large numbers of loci is necessary to detect a signal of
covariance in allele frequency changes when both drift (inflated in
evolve-and-sequence studies which use small population sizes) and sampling
variance can create spurious covariances. To address this limitation, we
calculated temporal covariances over 100kb genomic windows, with on average XXX
loci per window. While the covariance of each tile is noisy, we can analyze the
genome-wide distribution of tile covariances for changes through time. We would
like to compare the distribution of these tile covariances to a neutral
expectation, but using a theoretic neutral null distribution would be
inappropriate given complex dependencies across the genome due to linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

@@

Using the \textcite{Barghi2019-qy} study's data, we used the empirical neutral
null to investigate whether there was a general trend for the temporal
covariance $\cov(\Delta p_t, \Delta p_{t+k})$ to be positive for small $k$ (as
expected under selection), but then become systematically negative for larger
$k$ (as would occur under evolutionary processes that reverse the fitness of
regions across the genome). Such a change in the fitness direction of
haplotypes would not be discernible from genome-wide covariances like those in
Figure \ref{fig:figure-1}. We find (Figure \ref{fig:figure-3} A and B), pooling
across all replicates (see Supplementary Figure
\ref{suppfig:barghi-offset-replicate-panels} for individuals replicates), that
windowed temporal covariances between close timepoints are skewed positive (a
heavy right tail), while between more distant timepoints these windowed
temporal covariances tend to shift to become more negative (a heavy left tail).
We additionally quantified the degree to which the left and right tails change
as we look at covariances between timepoints further apart (Figure
\ref{fig:figure-3} C). We find that for covariances 2 timepoints apart ($k=2
\times 10$ generations), the $20\%$ right tail is inflated by a of 1.3 (95\% CI
[1.29, 1.32]), consistent with linked selection creating positive covariance in
allele frequency change. Under constant directional selection, we expect these
positive covariances between increasingly distant timepoints to decay to zero
as additive genetic variance is exhausted by selection and linkage
disequilibrium decays. Instead we find that for covariances 4 timepoints apart
($k=4 \times 10$ generations), the left tail of negative covariances is
inflated by a factor of 1.19 (95\% CI [1.17, 1.21]). Overall, we see a striking
pattern that covariances not only decay towards zero, but in fact become
negative through time, consistent with some regions in the genome having had a
reversed fitness effect at later timepoints.

@@

@@

\subsection{Variance-Covariance Matrix Correction}

@@

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/barghi-tailprobs-panels.pdf}

  \caption{ }
  \label{suppfig:barghi-tailprobs-panels}
\end{figure}

>>>>

% TODO
% - we have inconsistent notation between intro of results and figure 1 with
%   cov()

@@

We first analyzed \textcite{Barghi2019-qy}, an evolve-and-resequence study with
ten replicate populations exposed to a high temperature lab environment and
evolved for 60 generations, and sequenced every ten generations. Using the
seven timepoints and ten replicate populations, we estimated a bias-corrected
genome-wide $6 \times 6$ temporal covariance matrix $\mathbf{Q}$ for each of
the ten replicates (see Supplementary Material Sections
\ref{supp:ind-depth-var-corr} and \ref{supp:matrix-correction} for details on
the bias correction). Since the \textcite{Barghi2019-qy} study sequenced each
replicate population every ten generations, we calculate the temporal
covariance matrix over ten-generation allele frequency changes, which we write
as $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$. The diagonal elements of
this temporal covariance matrix are the sum of all variances in allele
frequency changes and pairwise covariances, e.g. element $\mathbf{Q}_{t,t} =
\sum_{i=t}^{9} \var(\Delta p_i) + 2\sum_{i \ne j} \cov(\Delta p_i, \Delta
p_j)$. Each off-diagonal element $\mathbf{Q}_{t,s}, \; t \ne s$ contains the
sum of pairwise covariances, $\mathbf{Q}_{t,s} = \sum_{i=t}^{t+9}
\sum_{j=s}^{s+9} \cov(\Delta p_i, \Delta p_j)$ (see Supplementary Material
Section \ref{supp:barghi-covs} for more details). These off-diagonal
covariances are expected to be zero when only drift is acting in the
population, as only linked selection can create covariance between allele
frequency changes \parencite{Buffalo2019-io}. Furthermore, since we cannot
directly observe the temporal covariances between adjacent timepoints, but only
the sums of temporal covariances, we expect the off-diagonal elements of
$\mathbf{Q}$ to be weak. This is because the magnitude of a temporal covariance
$\cov(\Delta p_i, \Delta p_j)$ is governed by the level of additive genetic
variance and linkage disequilibrium that persists after $|i-j|$ generations of
decay, which in \textcite{Barghi2019-qy}'s study design is on average 10
generations.

@@

Still, averaging across the ten temporal covariances matrices, we find positive
temporal covariances across time that are statistically significant (95\% block
bootstraps for all first off-diagonal elements do not contain zero), consistent
with linked selection perturbing allele frequency changes over very short time
periods. We visualize these covariances in Figure \label{figure-1} (A), which
depicts the temporal covariances through time, for each of the five
off-diagonal rows temporal covariance matrix. Each row represents the temporal
covariance $\cov(\Delta_{_{10}} p_s, \Delta_{_{10}} p_t)$, between some initial
reference generation $s$ (the row of the matrix), and some later timepoint $t$
(the column of the matrix). For each row, the covariances at first are
positive, and then decay towards zero as expected when directional selection
affects linked variants' frequency trajectories until ultimately linkage
disequilibrium and additive genetic variance for decay
\parencite{Buffalo2019-io}. Note that per replicate, the signal is a bit
noisier; see Supplementary Figures XXX.

While the presence of positive temporal covariances is consistent with linked
selection affecting allele frequencies over time, this measure not easily
interpretable. Additionally, we can quantify the impact of linked selection on
allele frequency change as the ratio of total covariance in allele frequency
change to the total variance in allele frequency change. Since the total
variation in allele frequency change can be decomposed into variance and
covariance components, $\var(p_t - p_0) = \sum_{i \ne j} \cov(\Delta p_i,
\Delta p_j) / \var(p_t - p_0)$, and the covariances are zero when drift acts
alone, this is a lower bound on how much of the variance in allele frequency
change is caused by linked selection \parencite{Buffalo2019-io}. We call this
measure $G(t)$, which is a lower bound on the total effect of linked selection
between the initial generation $0$ and some later generation $t$, which can be
varied to see how this quantity grows through time. As with the temporal
covariances, the study design of \textcite{Barghi2019} leads our measure $G(t)$
to be even more conservative, since the temporal covariances with each
ten-generation block between sequenced timepoints are not directly observable,
and are not included in the numerator of $G(t)$. Still, we find a remarkably
strong signal that greater than $20\%$ of total variation in allele frequency
change over 60 generations is directly the result of linked selection.

@@

\begin{align}
  \label{eq:conv-corr}
  \mathrm{cor}(\Delta p_s, \Delta p_t) = \frac{\E_{A\ne B} \left( \cov(\Delta p_{s,A}, \Delta p_{t,B}) \right)}{\E_{A\ne B} \left( \sqrt{\var(\Delta p_{s,A}) \var(\Delta p_{t,B})} \right)}
\end{align}
%
where $A$ and $B$ here are two replicate labels, and for the
\textcite{Barghi2019-qy} data, we use $\Delta_{_{10}} p_t$.

We've calculated the convergent correlation for all rows of the replicate
covariance matrices, which unlike temporal covariance matrices have diagonal
elements that are also covariances (e.g. $\cov(\Delta_{_{10}} p_{t,A},
\Delta_{_{10}} p_{t,B})$). Like temporal covariances, we visualize these
through time (Figure \ref{fig:figure-2} A), with each line representing the
convergent correlation from a particular reference generation $s$ as it varies
with $t$ (shown on the x-axis). In other words, each of the colored lines
corresponds to the like colored row of the convergence correlation matrix
(upper left in Figure \ref{fig:figure-2} A). We find these decay very quickly,
from an initial convergence correlation coefficient of about 0.1 (95\% block
bootstrap confidence intervals $[0.094,  0.11]$), to around 0.01 (95\% CIs
[0.0087, 0.015]) within 20 generations.

A benefit of between-replicate covariances is unlike temporal covariances,
these can be calculated with only two sequenced timepoints and a replicated
study design. This allowed allowed us to assess the impact of linked selection
in driving convergent patterns of allele frequency change across replicate
populations in two other studies. First, we reanalyzed the selection experiment
of \textcite{Kelly2019-dc}, which evolved three replicate populations of
\emph{Drosophila simulans} for 14 generations in a novel laboratory
environment. Since each replicate was exposed to the same selection pressure
and share linkage disequilibria common to the original natural founding
population, we expected each of the three replicate populations to have
positive between-replicate covariances. We find all three pairwise
between-replicate covariances are positive and statistical significant (95\%
CIs, [0.0063, 0.0086], [0.0064, 0.0086], [0.0061, 0.0083]). We estimate the
convergent correlation coefficient across these replicates as 0.36 ($95\%$
block-bootstrap confidence interval $[0.31, 0.40]$).

@@

Finally, we observed that in the longest run evolve-and-resequence study we
analyzed \parencite{Barghi2019-qy}, some temporal covariances appeared to
become negative at future timepoints (see the first two rows in Figure
\ref{fig:figure-1} A). This could be caused by advantageous fitness backgrounds
later becoming disadvantageous, either due to frequency-dependent selection,
recombination breaking up coupled beneficial and deleterious alleles, or an
environmental change in the direction of selection. However, the signal of a
change in the direction of selection localized to a particular region of the
genome may be washed out when we calculate genome-wide temporal covariances.
Averaging over such large numbers of loci is necessary to detect a signal of
covariance in allele frequency changes when both drift (inflated in
evolve-and-sequence studies which use small population sizes) and sampling
variance can create spurious covariances. To address this limitation, we
calculated temporal covariances over 100kb genomic windows (mean loci per
window 4,606, median 4,830). While the covariance of each tile is noisy, we can
analyze the genome-wide distribution of tile covariances for changes through
time. We would like to compare the distribution of these tile covariances to a
neutral expectation, but using a theoretic neutral null distribution would be
inappropriate given complex dependencies across the genome due to linkage
disequilibria (which can occur over long physical distances in E\&R and
selection studies, \cite{Nuzhdin2013-gf,Baldwin-Brown2014-cl}).

@@

Using the \textcite{Barghi2019-qy} study's data, we used the empirical neutral
null to investigate whether there was a general trend for the temporal
covariance $\cov(\Delta p_t, \Delta p_{t+k})$ to be positive for small $k$ (as
expected under selection), but then become systematically negative for larger
$k$ (as would occur under evolutionary processes that reverse the fitness of
regions across the genome). Such a change in the fitness direction of
haplotypes would not be discernible from genome-wide covariances like those in
Figure \ref{fig:figure-1}. We find (Figure \ref{fig:figure-3} A and B), pooling
across all replicates (see Supplementary Figure
\ref{suppfig:barghi-offset-replicate-panels} for individuals replicates), that
windowed temporal covariances between close timepoints are skewed positive (a
heavy right tail), while between more distant timepoints these windowed
temporal covariances tend to shift to become more negative (a heavy left tail).
We additionally quantified the degree to which the left and right tails change
as we look at covariances between timepoints further apart (Figure
\ref{fig:figure-3} C). We find that for covariances 2 timepoints apart ($k=2
\times 10$ generations), the $20\%$ right tail is inflated by a of 1.3 (95\% CI
[1.29, 1.32]), consistent with linked selection creating positive covariance in
allele frequency change. Under constant directional selection, we expect these
positive covariances between increasingly distant timepoints to decay to zero
as additive genetic variance is exhausted by selection and linkage
disequilibrium decays. Instead we find that for covariances 4 timepoints apart
($k=4 \times 10$ generations), the left tail of negative covariances is
inflated by a factor of 1.19 (95\% CI [1.17, 1.21]). This finding is also
robust to sign-permuting allele frequency changes on a chromosome-level, the
longest extent that gametic linkage disequilibria can extend (Supplementary
Figure \ref{suppfig:barghi-tailprobs-seqid}). Overall, we see a striking
pattern that covariances not only decay towards zero, but in fact become
negative through time, consistent with some regions in the genome having had a
reversed fitness effect at later timepoints.

@@

% \section{Materials and Methods}

% \subsection{Bias Correction}
% \subsection{}

@@

\subsection{Variance-Covariance Matrix Correction}
\label{supp:matrix-correction}

@@

\subsection{\textcite{Barghi2019-qy} Temporal Covariances}
\label{supp:barghi-covs}

Since each replicate population was sequenced every ten generations,
the timepoints $t_0 = 0$ generations, $t_1 = 10$ generations, $t_2 = 20$
generations, etc., lead to observed allele frequency changes across ten
generation blocks, $\Delta p_{t_0}, \Delta p_{t_1}, \ldots, \Delta p_{t_6}$.
Consequently, the ten temporal covariance matrices for each of the ten
replicate populations have off-diagonal elements of the form $\cov(\Delta
p_{t_0}, \Delta p_{t_1}) = \cov(p_{t_1} - p_{t_0}, p_{t_2} - p_{t_1}) =
\sum_{i=0}^{10} \sum_{j=10}^{20} \cov(\Delta p_i, \Delta p_j)$. Each diagonal
element has the form $\var(\Delta p_{t_0}) = \sum_{i=0}^{t_0} \var(\Delta
p_{i}) + \sum_{i \ne j}^{t_0} \cov(\Delta p_{i}, \Delta p_{j})$, and is thus a
combination of the effects of drift and selection, as both the variance in
allele frequency changes and cumulative temporal autocovariances terms increase
the variance in allele frequency. With sampling each generation, one could more
accurately partition the total variance in allele frequency change
\parencite{Buffalo2019-io}; while we cannot directly estimate the contribution
of linked selection to the variance in allele frequency change here, the
presence of a positive observed covariance between allele frequency change can
only be caused linked selection.

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/barghi-tailprobs-panels.pdf}
  \caption{}
  \label{suppfig:barghi-tailprobs-panels}
\end{figure}

\begin{figure}[!ht]
  \centering

  \includegraphics[]{figures/barghi-tailprobs-seqid-20.pdf}

  \caption{The 20\% lower and upper tail probabilities for the observed
  windowed covariances from the \textcite{Barghi2019-qy} study, based on
  sign-permuting at the chromosome level. This permutation empirical null
  is robust to long-range linkage disequilibrium acting over entire chromosomes.}

  \label{suppfig:barghi-tailprobs-seqid}
\end{figure}

\subsection{\textcite{Bergland2014-ij} Re-Analysis}

We also applied our temporal covariance approach to \textcite{Bergland2014-ij},
a study that finds evidence of genome-wide fluctuating selection between Spring
and Fall seasons across three years. As described in \textcite{Buffalo2019-io},
we would expect positive covariances between like seasons (i.e. Spring 2010 and
Spring 2011), and negative covariances between dislike seasons (i.e. Spring
2010 and Fall 2011) when fluctuating selection is strong and acts genome-wide,
as the original study found. However, while we find temporal covariances that
are non-zero, we find only weak support for a seasonal fluctuating model
driving these covariances. In Supplementary Figure XXX, we show the temporal
covariances from varying reference generations, across Spring/Fall,
Spring/Spring, and Fall/Fall pairs. The first row of temporal covariance matrix
is consistent with fluctuating selection operating for two timepoints, as the
first covariance is negative, and the second is positive, and later covariances
are not statistically differentiable from zero (which could occur if LD and
additive genetic variance decay). However, the all other temporal covariances
do not fit the pattern we would expect under genome-wide fluctuating selection.

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/bergland_pvalues.pdf}

  \caption{A: Scatterplot of the original unadjusted p-values from
    \textcite{Bergland2014-ij} and the p-values from our reanalysis of the same
    data using the same statistical methods; the minor discrepancy is likely due to software
    version differences. B: The histograms of the p-values of our reanalysis
    and the original \textcite{Bergland2014-ij} data; again the minor
    discrepancy is likely due to software differences. Overall, our
    implementation of Bergland et al.'s statistical methods produces results 
    very close to the original analysis.}

  \label{suppfig:bergland-pvalue-comparison}
\end{figure}

We were concerned that this might be due to a flaw in our methods. To address
this concern, we first ensured that our temporal-covariance matrix bias
correction was working as expected. We find that it corrects the relationship
between depth and both variance and covariance (Supplementary Figure XXX) as
expected. We then re-analyzed the data of \parencite{Bergland2014-ij} using the
same seasonal fluctuating model as the original paper. This model is a Binomial
logit-linked GLM fit per-locus, where the Spring/Fall seasons are encoded as a
dummy variable, and are regressed on the frequency data. We use the same
binomial weighting procedure as \textcite{Bergland2014-ij}, where the weights
are determined by the effective number of chromosomes, $N_{eff} = (2 n_t d_t -
1) / (2 n_t + d_t)$ ($n_t$ and $d_t$ are the number of diploid individuals and
the read depth at timepoint $t$, respectively). We fit this model on all loci
marked as used in the VCF provided with the \textcite{Bergland2014-ij} study
(doi:10.5061/dryad.v883p). Overall, our p-values for the Wald test for each
locus closely match those of the original paper (Pearson correlation
coefficient 0.98, p-value < $2.2 \times 10^{-16}$; see Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} A), and the histograms of the p-values
are nearly identical (Supplementary Figure
\ref{suppfig:bergland-pvalue-comparison} B).

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/bergland-pvalue-permutation-hist.pdf}
  \caption{}
  \label{suppfig:bergland-pvalue-hist}
\end{figure}

While \textcite{Bergland2014-ij} find loci with a significant association with
season after a Benjamini and Hochberg FDR p-value adjustment
\parencite{Benjamini1995-jy}, they do not construct a null distribution of
p-values as would be expected if fluctuating selection were not acting. Without
such a distribution, we do not have a statistical expectation for the number of
variants across the genome with frequency trajectories that spuriously fit the
pattern of seasonal fluctuating selection. We found that we can create this
empirical null distribution by randomly permuting the season labels and
re-running the per-locus seasonal GLM model. We find, regardless of whether we
permute at the locus-level or the permutation replicate-level, that the
observed seasonal p-value distribution \textcite{Bergland2014-ij} is not
enriched for significant p-values beyond what we would expect from the
permutation null. In fact, there appears there is more enrichment for low
p-values when seasonal labels are randomly permuted (Supplementary Figure
\ref{suppfig:bergland-pvalue-hist}, suggesting by random chance we might expect
more variants with a seasonal fluctuating pattern than found in the original
\textcite{Bergland2014-ij} study. While surprising, this could be explained by
the presence of temporal structure across the samples not consistent with
seasonal fluctuating selection. Some fraction of the $\nicefrac{6!}{(6-2)!} =
30$ permutations happen to fit this structure well, leading to an enrichment of
small p-values. This non-seasonal temporal structure is also evident in our
temporal covariances (Supplementary Figure XXX), where we see strong evidence
of selection (non-zero temporal covariances), yet the pattern does not follow
that of seasonal fluctuating selection.
